Results

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

## Validity of subjective values of ER strategies

>>>>

## Ecological validity of subjective values of ER strategies

Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
Greater variability might even adaptive [@Blanke2020;@Aldao2015].
In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020].
Thus, different factors have only rarely been studied together[@Young2020].
Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) cannot be used to determine what internal subjective value the subjects associated with the strategies.
However, we succeeded in this with our new CAD paradigm.
On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.

## Trait character of SVs
Hat das Trait-Charakter?

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).

>>>>

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
